\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{booktabs}

% Geometry
\geometry{top=0.6in, bottom=0.6in, left=0.75in, right=0.75in}

% Custom colors
\definecolor{linkcolor}{HTML}{1A73E8}
\hypersetup{
    colorlinks=true,
    urlcolor=linkcolor,
    linkcolor=linkcolor,
    filecolor=linkcolor,
    citecolor=linkcolor
}

% Section formatting (adjusted for better spacing)
\titleformat{\section}{\large\bfseries\sffamily}{}{0em}{\color{black}\titlerule[0.8pt]\vspace{4pt}} % Horizontal rule and spacing
\titlespacing{\section}{0pt}{4pt}{4pt} % Adjusted spacing before and after sections

% Custom commands
\newcommand{\entry}[2]{\textbf{#1}\hfill #2}
\newcommand{\subentry}[2]{\textit{#1}\hfill #2}

\begin{document}

% Header
\begin{center}
    {\LARGE \textbf{Aman Kumar Singh}} \\
    \vspace{4pt}
    \href{mailto:amankrsingh227@gmail.com}{amankrsingh227@gmail.com} \textbullet{}
    +91 9266655548 \textbullet{} New Delhi, India \\
    \vspace{4pt}
    \href{https://amankrsingh.vercel.app/}{Portfolio} \textbullet{}
    \href{https://github.com/amanrathore48}{GitHub} \textbullet{}
    \href{https://linkedin.com/in/aman-kr-singh}{Linkedin}
\end{center}

% Education
\section*{Education}
\entry{B.Tech. in Mechatronics}{Delhi Institute of Tool Engineering \textbullet{} 2019 -- 2023}
\begin{itemize}[leftmargin=0.5cm]
    \item CGPA: 8.49/10
\end{itemize}

\entry{Class XII (CBSE)}{Lions Public School \textbullet{} 2018 -- 2019}
\begin{itemize}[leftmargin=0.5cm]
    \item Percentage: 84.6%
\end{itemize}
\vspace{2pt}

% Professional Experience
\section*{Professional Experience}
\entry{Software Developer | Digital India Corporation}{Aug 2023 -- Present}
\begin{itemize}[leftmargin=0.5cm]
    \item Spearheaded the development of the new \textbf{ApiSetu admin portal}, enabling organization login and verification.
    \item Implemented \textbf{data encryption protocols} for APIs, ensuring secure data transmission and compliance with best practices.
    \item Designed and integrated \textbf{highly reusable and customizable components}, reducing development time by an estimated 30%.
    \item Optimized \textbf{data retrieval mechanisms} using \textbf{SWR} and \textbf{Next.js server-side rendering}, improving application performance.
\end{itemize}

\entry{Full Stack Developer (Intern) | DigiLocker}{ Dec 2022 -- Mar 2023}
\begin{itemize}[leftmargin=0.5cm]
    \item Executed CRUD operations to ensure seamless data manipulation and database interaction.
    \item Fortified platform security by implementing \textbf{NextAuth} for authentication.
    \item Integrated \textbf{MongoDB} and \textbf{MySQL} databases with \textbf{Prisma} for streamlined data management.
\end{itemize}

\entry{MERN Stack Developer | Creatospace}{Jun 2022 -- Dec 2022}
\begin{itemize}[leftmargin=0.5cm]
    \item Designed and developed a user-friendly product interface in a startup environment.
    \item Engineered a referral system and integrated a payment gateway, enhancing functionality.
    \item Adopted \textbf{MVC-based code architecture} for maintainability.
\end{itemize}
\vspace{2pt}

% Projects
\section*{Projects}
\entry{Ecomm: E-commerce Website}{\href{https://ecomm-eight-pearl.vercel.app/}{Live} \textbullet{} \href{https://github.com/amanrathore48/Ecomm.}{GitHub}}
\begin{itemize}[leftmargin=0.5cm]
    \item Built with \textbf{Next.js}, \textbf{Tailwind CSS}, \textbf{MongoDB}, and \textbf{NextAuth}.
    \item Implemented advanced filtering, search, and secure checkout processes.
\end{itemize}

\entry{InfoSynth: Information Synthesis Web App}{\href{https://infosynthai.netlify.app/}{Live} \textbullet{} \href{https://github.com/amanrathore48/InfoSynth}{GitHub}}
\begin{itemize}[leftmargin=0.5cm]
    \item Utilized \textbf{React} and \textbf{ChatGPT API} to summarize articles efficiently.
    \item Designed with \textbf{Tailwind CSS} for a sleek, modern interface.
\end{itemize}

\entry{Minicraft: Light Game}
{\href{https://minicarft.netlify.app/}{Live} \textbullet{} 
\href{https://github.com/amanrathore48/Minicraft}{GitHub}}
\begin{itemize}[leftmargin=0.5cm]
    \item Built with \textbf{React.js} and \textbf{Three.js} to simulate Minecraft-like gameplay.
\end{itemize}
\vspace{2pt}

% Skills
\section*{Skills}
\begin{multicols}{2}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Languages:} C++, JavaScript, Python, TypeScript
    \item \textbf{Frameworks:} React, Next.js, NestJS, Express
    \item \textbf{Tools:} Docker, AWS, Git/GitHub, Postman
    \item \textbf{Databases:} MongoDB, MySQL, Prisma
    \item \textbf{Problem-Solving:} Solved 270+ DSA problems on LeetCode
\end{itemize}
\end{multicols}

\end{document}
